---
title: "HW6"
author: "Tong Hao"
format: html
embed-resources: true
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(gt)
library(ISLR2)
library(usethis)
```

## Problem 1
**Step 1: State Hypothesis**

Null hypothesis: $H_0: \mu = 110 \ (\$)$  
Alternative hypothesis: $H_a: \mu \neq 110 \ (\$)$

```{r}
glimpse(ISLR2::Carseats)
mean(ISLR2::Carseats$Price,
     na.rm = TRUE)
mean
```
The mean price is 115.795.

**Step 2: Relevant Visualization**
```{r}
ggplot(ISLR2::Carseats, aes(x = Price)) +
  geom_histogram(fill = "darkgreen", color = "white") +
  labs(x = "Price",
       y = "Frequency",
       title = "Histogram of Price of Child Carseat") +
  theme_minimal()
```
The distribution is mostly to the right of 100.

```{r}
t.test(ISLR2::Carseats$Price,
       mu = 110)
```

**Step 3: Conclusion**
Here, the t-statistic of 10.56 means that the sample mean is far away from the hypothesized mean, since t-statistic of 0 means that the sample mean is equal to the hypothesized mean. The t-statistic of 10.56 indicates that there are many standard error deviated from the 110. The p-value of 2.2e-16 is extremely small, suggesting that our data is very unlikely if the average price is 110 The data provides strong evidence that the mean price is not 110. Therefore, we reject $H_0: \mu = 110 \ (\$)$.

## Problem 2
```{r}
mean(ISLR2::Carseats$CompPrice,
     na.rm = TRUE)
```

```{r}
result <- t.test(ISLR2::Carseats$CompPrice,
       conf.level = 0.90)
result

str(result)
```

```{r}
moe <- (result$conf.int[2] - result$conf.int[1])/2
moe
```
The 90% confidence interval for mean competitor price is in between 123.7109 and 126.2391.
The sample mean is 124.975.
The margin of error is 1.26.

## Problem 3
```{r}
glimpse(penguins)

species_island <- table(penguins$species, penguins$island)

addmargins(species_island)
```

## Problem 4
create_github_token()
gitcreds::gitcreds_set()
use_github()

The clickable link is: https://github.com/haotttttt/HW6.git.

